Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-02-08 analysis/paper/paper.Rmd
plot crammer with confidence intervals

```{r, results='asis'}
st_options('bootstrap.css', FALSE)
rdb %>% select()
ctable(rdb$d_centres_country %>% sapply(function(x){
  as.character(x) %>% factor()
}), rdb$q_340_insects%>% sapply(function(x){
  as.character(x) %>% factor()
}), style = 'rmarkdown',
       useNA = "no",
       prop = "r",
       totals = F,
       round.digits = 1,
dnn = c("Countries","Insects"))

@@

Patients who underent anaphylaxis due to insect venom more often experienced 
cardiologic symptoms. Especially collapsing due to hypotension was prominently 
more often seen in patient who underwent venom anaphylaxis. This difference was especially visible in children under the age of 18 years.

@@

>>>>

```{r, results='asis'}
st_options('bootstrap.css', FALSE)
#rdb %>% select()
ctable(rdb$d_centres_country %>% sapply(function(x){
  as.character(x) %>% factor()
}), rdb$q_340_insects%>% sapply(function(x){
  as.character(x) %>% factor()
}), style = 'rmarkdown',
       useNA = "no",
       prop = "r",
       totals = F,
       round.digits = 1,
dnn = c("Countries","Insects"))

```
```{r}
plot.proportions(rdb, "d_centres_country","q_340_insects")

@@

Patients who underent anaphylaxis due to insect venom more often experienced 
cardiologic symptoms. Especially collapsing due to hypotension was prominently 
more often seen in patient who underwent venom anaphylaxis. This difference was especially visible in children under the age of 18 years. (See the ade adapted symptoms plot). 
We saw prominent differences in association of specific symptoms with eliocitor in cerain age groups. Children under 13 yoears of age showed association with IVIA and vomiting - whereas adults did not. Hypotension collapse was more prominently associated with IVIA in children whereas loss of consciousness in adults.

@@

```{r}
plot.Cramer(supraCramerFun(data =rdbp,
               vars =c( "q_114",
               "q_112_incontinence",
               "q_114_dizziness",
               "q_112_abdominal_pain",
               "q_114_loss_of_consciousness",
               "q_114_hypotension_collapse_v5",
               "q_114_reductions_of_alertness",
               "q_111_angioedema",
               "q_113_wheezing_expiratory_distress_v5"),
               grouping = "grouping",
               subset = "d_age_gr2"))

```{r}
plot.Cramer(cramerFun(data =rdbp,
               vars=c("q_114",
               "q_112_incontinence",
               "q_114_dizziness",
               "q_112_abdominal_pain",
               "q_114_loss_of_consciousness",
               "q_114_hypotension_collapse_v5",
               "q_114_reductions_of_alertness",
               "q_111_angioedema",
               "q_113_wheezing_expiratory_distress_v5"),
               grouping = "grouping"))
```

```{r}
tryptase_plot(rdb)+
  scale_x_log10()
